---
title: "Week 9 class 3 - Chaos and Fractals"
author: "Phileas Dazeley-Gaist"
date: "03/02/2022"
theme: cerulean
output:
  pdf_document:
    highlight: default
    keep_tex: no
    fig_caption: yes
    latex_engine: pdflatex
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(ggrepel)
library(magic)
library(lubridate)
library(zeallot)

clear_theme <- theme(legend.position="none",
            panel.background = element_rect(fill="white"),
            plot.margin=grid::unit(c(1,1,0,0), "mm"),
            panel.grid=element_blank(),
            axis.ticks=element_blank(),
            axis.title=element_blank(),
            axis.text=element_blank())
```

## Today's goals

- Strange attractors, (1D vs 2D vs 3D)
- Ice (interlude)
- Drawing

## R Lorenz attractor

The behaviour of strange attractors is limited by the spacial dimension of the space it inhabits. In two dimensions: a continuous infinite curve cannot be chaotic, it has to end in a cycle or a fixed point. This is known as the Poincaré-Bendixson theorem. 

1D - Only one direction. If space is bounded, fixed points.
2D - Only two directions. If space is bounded, cycles or fixed points.
3D - 3 directions. If space is bounded, you can still have chaotic orbits. You can also get cycles or fixed points.

Here is code for a Lorenz attractor plotter in r

```{r}

```

## Drawing

